### 2024-03-10 paper/paper.qmd
created some tables and figures for the paper.qmd

---
title: "My title"
subtitle: "My subtitle if needed"
author: 
  - First author
  - Another author
thanks: "Code and data are available at: LINK."
date: today
date-format: long
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format: pdf
number-sections: true
bibliography: references.bib
---

```{r}
#| include: false
#| warning: false
#| message: false

library(tidyverse)
library(rstanarm)
library(arrow)
```

# Introduction

You can and should cross-reference sections and sub-sections. We use @citeR and @rohan.

The remainder of this paper is structured as follows. @sec-data....

# Data {#sec-data}

Some of our data is of penguins (@fig-bills), from @palmerpenguins.

```{r}
#| label: fig-bills
#| fig-cap: Bills of penguins
#| echo: false

ggplot(penguins, aes(x = island, fill = species)) +
  geom_bar(alpha = 0.8) +
  scale_fill_manual(values = c("darkorange","purple","cyan4"),
                    guide = "none") +
  theme_minimal() +
  facet_wrap(~species, ncol = 1) +
  coord_flip()
```

Talk more about it.

And also planes (@fig-planes). (You can change the height and width, but don't worry about doing that until you have finished every other aspect of the paper - Quarto will try to make it look nice and the defaults usually work well once you have enough text.)

```{r}
#| label: fig-planes
#| fig-cap: Relationship between wing length and width
#| echo: false
#| warning: false
#| message: false

analysis_data <- read_csv(here::here("data/analysis_data/analysis_data.csv"))

analysis_data |> 
  ggplot(aes(x = width, y = length)) +
  geom_point(alpha = 0.8) +
  theme_minimal() +
  labs(x = "Wing width (mm)",
       y = "Wing length (mm)")
```

Talk way more about it.

# Model

The goal of our modelling strategy is twofold. Firstly,...

Here we briefly describe the Bayesian analysis model used to investigate... Background details and diagnostics are included in [Appendix -@sec-model-details].

## Model set-up

Define $y_i$ as the number of seconds that the plane remained aloft. Then $\beta_i$ is the wing width and $\gamma_i$ is the wing length, both measured in millimeters.

\begin{align} 
y_i|\mu_i, \sigma &\sim \mbox{Normal}(\mu_i, \sigma) \\
\mu_i &= \alpha + \beta_i + \gamma_i\\
\alpha &\sim \mbox{Normal}(0, 2.5) \\
\beta &\sim \mbox{Normal}(0, 2.5) \\
\gamma &\sim \mbox{Normal}(0, 2.5) \\
\sigma &\sim \mbox{Exponential}(1)
\end{align}

We run the model in R [@citeR] using the `rstanarm` package of @rstanarm. We use the default priors from `rstanarm`.

### Model justification

We expect a positive relationship between the size of the wings and time spent aloft. In particular...

We can use maths by including latex between dollar signs, for instance $\theta$.

# Results

Our results are summarized in @tbl-total_coded_modelresults and @tbl-referred_informed_modelresults.

```{r}
#| echo: false
#| eval: true
#| warning: false
#| message: false

library(rstanarm)

total_coded_model <-
  readRDS(file = here::here("models/total_coded_model.rds"))

referred_informed_model <-
  readRDS(file = 
            here::here("models/referred_informed_model.rds"))
```

```{r}
#| echo: false
#| eval: true
#| label: tbl-total_coded_modelresults
#| tbl-cap: "Explanatory model of homeless death count in relation to total number of helpline calls coded per month"
#| warning: false

modelsummary::modelsummary(
  list(
    "Total Coded Model" = total_coded_model
  ),
  statistic = "mad",
  fmt = 3
)
```

```{r}
#| echo: false
#| eval: true
#| label: tbl-referred_informed_modelresults
#| tbl-cap: "Explanatory model of homeless death count in relation to the number of homeless referred to shelters and provided with information on homelessness prevention per month"
#| warning: false

modelsummary::modelsummary(
  list(
    "Referred and Informed Model" = referred_informed_model
  ),
  statistic = "mad",
  fmt = 3
)
```

# Discussion

## First discussion point {#sec-first-point}

If my paper were 10 pages, then should be be at least 2.5 pages. The discussion is a chance to show off what you know and what you learnt from all this.

## Second discussion point

## Third discussion point

## Weaknesses and next steps

Weaknesses and next steps should also be included.

\newpage

\appendix

# Appendix {.unnumbered}

# Additional data details

# Model details {#sec-model-details}

## Posterior predictive check

In @fig-ppcheckandposteriorvsprior-1 we implement a posterior predictive check. This shows...

In @fig-ppcheckandposteriorvsprior-2 we compare the posterior with the prior. This shows...

```{r}
#| eval: true
#| echo: false
#| message: false
#| warning: false
#| label: fig-ppcheckandposteriorvsprior
#| layout-ncol: 2
#| fig-cap: "Examining how the model fits, and is affected by, the data"
#| fig-subcap: ["Posterior prediction check", "Comparing the posterior with the prior"]
library(ggplot2)

pp_check(total_coded_model) +
  theme_classic() +
  theme(legend.position = "bottom")

posterior_vs_prior(total_coded_model) +
  theme_minimal() +
  scale_color_brewer(palette = "Set1") +
  theme(legend.position = "bottom") +
  coord_flip()
```

```{r}
#| eval: true
#| echo: false
#| message: false
#| warning: false
#| label: fig-ppcheckandposteriorvsprior
#| layout-ncol: 2
#| fig-cap: "Examining how the model fits, and is affected by, the data"
#| fig-subcap: ["Posterior prediction check", "Comparing the posterior with the prior"]
library(ggplot2)

pp_check(referred_informed_model) +
  theme_classic() +
  theme(legend.position = "bottom")

posterior_vs_prior(referred_informed_model) +
  theme_minimal() +
  scale_color_brewer(palette = "Set1") +
  theme(legend.position = "bottom") +
  coord_flip()
```

## Diagnostics

@fig-total_coded_model_stanareyouokay-1 is a trace plot. It shows... This suggests...

@fig-total_coded_model_stanareyouokay-2 is a Rhat plot. It shows... This suggests...

```{r}
#| echo: false
#| eval: true
#| message: false
#| warning: false
#| label: fig-total_coded_model_stanareyouokay
#| fig-cap: "Checking the convergence of the MCMC algorithm"
#| fig-subcap: ["Trace plot", "Rhat plot"]
#| layout-ncol: 2

plot(total_coded_model, "trace")

plot(total_coded_model, "rhat")
```

@fig-referred_informed_model_stanareyouokay-1 is a trace plot. It shows... This suggests...

@fig-referred_informed_model_stanareyouokay-2 is a Rhat plot. It shows... This suggests...

```{r}
#| echo: false
#| eval: true
#| message: false
#| warning: false
#| label: fig-referred_informed_model_stanareyouokay
#| fig-cap: "Checking the convergence of the MCMC algorithm"
#| fig-subcap: ["Trace plot", "Rhat plot"]
#| layout-ncol: 2

plot(referred_informed_model, "trace")

plot(referred_informed_model, "rhat")
```

\newpage

# References

### 2024-03-10 paper/paper.qmd
unknown error has occured, I cannot read files now, always shows up as "no such file exist".

@@
 format: pdf
+toc: true
 number-sections: true
@@
 library(arrow)
+library(knitr)
+library(ggplot2)
 ```
@@
 
-Some of our data is of penguins (@fig-bills), from @palmerpenguins.
-
+## Helpline Wrap-Up Codes Data
 ```{r}
-#| label: fig-bills
-#| fig-cap: Bills of penguins
+#| label: tbl-monthly-coded
+#| tbl-cap: Sample of monthly summation for Helpline Coded Calls data
 #| echo: false
 
-ggplot(penguins, aes(x = island, fill = species)) +
-  geom_bar(alpha = 0.8) +
-  scale_fill_manual(values = c("darkorange","purple","cyan4"),
-                    guide = "none") +
-  theme_minimal() +
-  facet_wrap(~species, ncol = 1) +
-  coord_flip()
+cleaned_data <- read_parquet("data/analysis_data/cleaned_data.parquet")
+
+sample_helpline <- cleaned_data |> select(Month_date, Total_Coded, Referred, Informed)
+
+sample_helpline <- head(sample_helpline)
+
+knitr::kable(sample_helpline, col.names = c("Month", "Calls Coded", "Referral to Shelter", "Homelessness Prevention Info"), align = c("l", "c", "c", "c"))
+```
+
+## Final Combined Dataset
+```{r}
+#| label: tbl-monthly-calls
+#| tbl-cap: Sample of monthly homeless death count and Helpline Coding efforts
+#| echo: false
+
+sample_cleaned_data <- head(cleaned_data)
+
+knitr::kable(sample_cleaned_data, col.names = c("Month", "Total Coded", "Referred to Shelter", "Homeless Info", "Death Count"), align = c("l", "c", "c", "c", "c"))
+
 ```
@@
 #| fig-subcap: ["Posterior prediction check", "Comparing the posterior with the prior"]
-library(ggplot2)
 

### 2024-03-10 paper/paper.qmd
added here::here to the readr function, previous issue is fixed

@@
 
-## Helpline Wrap-Up Codes Data
+## Central Intake Call Wrap-Up Codes
 ```{r}
@@
 
-cleaned_data <- read_parquet("data/analysis_data/cleaned_data.parquet")
+cleaned_data <- read_parquet(here::here("data/analysis_data/cleaned_data.parquet"))
 
@@
 ```
+## Deaths of People Experiencing Homelessness
+
+```{r}
+#| label: tbl-death-count
+#| tbl-cap: Sample of Cleaned Deaths of People Experiencing Homelessness Dataset
+#| echo: false
+
+sample_death_counts <- cleaned_data |> select(Month_date, Death_Count)
+
+sample_death_counts <- head(sample_death_counts)
+
+knitr::kable(sample_death_counts, col.names = c("Month", "Death Count"), align = c("c", "c"))
+```
 
@@
 ```{r}
-#| label: tbl-monthly-calls
+#| label: tbl-combined
 #| tbl-cap: Sample of monthly homeless death count and Helpline Coding efforts

### 2024-03-10 paper/paper.qmd
finished editted code for data section

@@
 (You can change the height and width, but don't worry about doing that until you have finished every other aspect of the paper - Quarto will try to make it look nice and the defaults usually work well once you have enough text.)
-
-```{r}
-#| label: fig-planes
-#| fig-cap: Relationship between wing length and width
-#| echo: false
-#| warning: false
-#| message: false
-
-analysis_data <- read_csv(here::here("data/analysis_data/analysis_data.csv"))
-
-analysis_data |> 
-  ggplot(aes(x = width, y = length)) +
-  geom_point(alpha = 0.8) +
-  theme_minimal() +
-  labs(x = "Wing width (mm)",
-       y = "Wing length (mm)")
-```
-
-Talk way more about it.
 

### 2024-03-11 paper/paper.qmd
modified the language used in data section from the old paper to suit the needs of the new paper

@@
 author: 
-  - First author
-  - Another author
+  - Sandy Yu
 thanks: "Code and data are available at: LINK."
@@
 
-The remainder of this paper is structured as follows. @sec-data....
+Analyses and findings in this paper are structured into several sections: @sec-data -- Data, @sec-model – Model, @sec-results -- Results, and @sec-discussion -- Discussion.
+The Data section examines all datasets and variables kept for analysis, followed by an explanation of their data cleaning processes.
+The Model section defines linear models used for further analysis, explain its components, and presents model justifications.
+The Result section focuses on visualizing and presenting the model results through data presented in Data section.
+The Discussion section further evaluate the interpretations behind the model results presented in the previous section, and touches on any weaknesses and next steps.
 
@@
 
+All data used in this paper are obtained through OpenDataToronto Portal [@OpenDataToronto].
+Two different datasets: Central Intake Call Wrap-Up Codes Data [@Central_Intake_Call] and Deaths of People Experiencing Homelessness[@Homeless_Death_Count], are retrieved to analyze the effect of Toronto’s Central Call Line (denoted as *Helpline* for the remainder of this paper) efforts to the death counts of homeless individuals in Toronto.
+Data is cleaned and analyzed using the open source statistical programming language R [@citeR] and supporting packages tidyverse [@tidyverse], janitor [@janitor], dplyr [@dplyr], rstanarm [@rstanarm], arrow [@arrow], ggplot2 [@ggplot2], and knitr [@knitr].
+Detailed description of each dataset can be found in the subsections below.
+
 ## Central Intake Call Wrap-Up Codes
+
+On the OpenDataToronto portal, there are several datasets that reflect the City’s effort to shelter the local homeless population.
+The Central Intake Call Wrap-Up Codes Dataset [@Central_Intake_Call], stored in the Central Intake Calls Catalogue [@Central_Intake_Call], is one of the freshest and most detailed.
+Data is stored and published by the Shelter, Support & Housing Administration since November of 2020 and refreshes on a monthly basis.
+The latest refresh occurred on January 15th, 2024.
+
+The data set provides a daily summary of the number of calls received, the number of calls classified into distinct wrap-up codes by the nature of its issue, and a count of calls under each wrap-up code.
+One of the example wrap-up codes in the original data set was: *Code 1A - Referral to a Sleeping/Resting Space*.
+The original data set includes 13 distinct wrap-up codes; only two codes, *Code 1A — Referral to a Sleeping/Resting Space* and *Code 2C — Information - Homelessness & Prevention Services*, were chosen for our analysis.
+Code 1A and Code 2C are best suited as measurements for positive impact the Central Intake Line could provide because they provide a count of the number of callers provided with directions or advice.
+Other non-suitable wrap-up codes include: *Code 1D - Declined Shelter/Resting Space*, *Code 4B - Disconnected - No Outcome*, etc.
+
+The final dataset only includes monthly cumulative data before July of 2023. The rationalization behind the action will be explained in @sec-combined-data.
+
 ```{r}
@@
 ```
+
 ## Deaths of People Experiencing Homelessness
+
+The Deaths of People Experiencing Homelessness Dataset [@Homeless_Death_Count] contains monthly cumulative records of homeless deaths.
+The dataset is published by Toronto Public Health [@TPH].
+The earliest data record started in January of 2017, and the latest record ends in June of 2023.
+
+The original dataset contains three columns: *Year of death*, *Month of death*, and *Count*.
+After careful inspection of raw data, any rows that containing an “unknown” value are excluded.
+Although this action created a source of error in future analyses, this is still a necessary step because we are plotting death counts against a timeline.
+
+Final dataset only includes data from November 2020 to June 2023 (@tbl-death-count). The rationalization behind the action will be explained in @sec-data-diff-datasets.
 
@@
 
-## Final Combined Dataset
+## Final Combined Data {#sec-combined-data}
+
+During the data cleaning process, code was written to ensure that both the Central Intake Call Wrap-Up Codes Dataset [@Central_Intake_Call] and the Deaths of People Experiencing Homelessness Dataset [@Homeless_Death_Count] are filtered to include only data between 1st November, 2020 to 30st June, 2023.
+
+The decision is reached by taking the common time period between the two datasets.
+In the latest refresh, the Central Intake Call Wrap-Up Codes Dataset [@Central_Intake_Call] begins on 3rd November, 2020 and end on 31st December, 2023; whereas the Deaths of People Experiencing Homelessness Dataset [@Homeless_Death_Count] begins on January of 2017 and ends on June 2023.
+
+The ultimate purpose of taking the common time period is to ensure that we can have the same amount of observations for analysis.
+Thus a combined dataset that kept the variables of interest in both datasets is created (@tbl-combined).
+
 ```{r}
@@
 
-Talk more about it.
-
-And also planes (@fig-planes).
-(You can change the height and width, but don't worry about doing that until you have finished every other aspect of the paper - Quarto will try to make it look nice and the defaults usually work well once you have enough text.)
-
-# Model
+# Model {#sec-model}
 
@@
 
-Here we briefly describe the Bayesian analysis model used to investigate... Background details and diagnostics are included in [Appendix -@sec-model-details].
+Here we briefly describe the Bayesian analysis model used to investigate the correlation between homeless death counts in Toronto and the efforts of the Helpline staff.
+Background details and diagnostics are included in [Appendix -@sec-model-details].
 
@@
 
-Define $y_i$ as the number of seconds that the plane remained aloft. Then $\beta_i$ is the wing width and $\gamma_i$ is the wing length, both measured in millimeters.
+Magnitude of effect created by the helpline efforts can be estimated through linear models.
 
-\begin{align} 
-y_i|\mu_i, \sigma &\sim \mbox{Normal}(\mu_i, \sigma) \\
-\mu_i &= \alpha + \beta_i + \gamma_i\\
-\alpha &\sim \mbox{Normal}(0, 2.5) \\
-\beta &\sim \mbox{Normal}(0, 2.5) \\
-\gamma &\sim \mbox{Normal}(0, 2.5) \\
-\sigma &\sim \mbox{Exponential}(1)
-\end{align}
+### Model 1: Total Coded Model
+
+$y_i|\mu_i$, $\sigma \sim \mbox{Normal}(\mu_i, \sigma)$
+
+$\mu_i = \alpha + \phi_i$
+
+$\alpha \sim \mbox{Normal}(0, 2.5)$
+
+$\phi \sim \mbox{Normal}(0, 2.5)$
+
+$\sigma \sim \mbox{Exponential}(1)$
+
+Where:
+
+-   $y_i$ is the number of homeless death count in Toronto recorded by @TPH per month
+
+-   $\phi_i$ is the total number of calls received and coded by the helpline per month
+
+### Model 2: Referred Informed Model
+
+$y_i|\mu_i$, $\sigma \sim \mbox{Normal}(\mu_i, \sigma)$
+
+$\mu_i = \alpha + \beta_i + \gamma_i$
+
+$\alpha \sim \mbox{Normal}(0, 2.5)$
+
+$\beta \sim \mbox{Normal}(0, 2.5)$
+
+$\gamma \sim \mbox{Normal}(0, 2.5)$
+
+$\sigma \sim \mbox{Exponential}(1)$
+
+Where:
+
+-   $y_i$ is the number of homeless death count in Toronto recorded by @TPH per month
+
+-   $\beta_i$ is the number of homeless individuals referred to shelters through the helpline, per month
+
+-   $\gamma_i$ is the number of individuals provided with information on homelessness prevention through the helpline, per month
 
@@
 
-### Model justification
+### Model justifications
 
-We expect a positive relationship between the size of the wings and time spent aloft. In particular...
+We expect a net negative relationship between the net efforts made by the helpline staff (Recorded by the Total_Coded column) and homeless death count, which implies that net effect of helpline calls **reduces** homeless death count in Toronto.
 
-We can use maths by including latex between dollar signs, for instance $\theta$.
+Additionally, we expect a negative relationship between homeless death and the number of homeless individuals referred to shelter & the number of individuals provided with homelessness prevention information.
+Since both factors are coded efforts made by the helpline, both factors should also help to reduce homeless death count in Toronto.
 
-# Results
+# Results {#sec-results}
 
@@
 
-# Discussion
+# Discussion {#sec-discussion}
 
@@
 
-In @fig-ppcheckandposteriorvsprior-1 we implement a posterior predictive check. This shows...
+In @fig-total_coded_model_ppcheckandposteriorvsprior-1 we implement a posterior predictive check. This shows...
 
-In @fig-ppcheckandposteriorvsprior-2 we compare the posterior with the prior. This shows...
+In @fig-total_coded_model_ppcheckandposteriorvsprior-2 we compare the posterior with the prior. This shows...
 
@@
 #| warning: false
-#| label: fig-ppcheckandposteriorvsprior
+#| label: fig-total_coded_model_ppcheckandposteriorvsprior
 #| layout-ncol: 2
@@
 
+In @fig-referred_informed_model_ppcheckandposteriorvsprior-1 we implement a posterior predictive check. This shows...
+
+In @fig-referred_informed_model_ppcheckandposteriorvsprior-2 we compare the posterior with the prior. This shows...
+
 ```{r}
@@
 #| warning: false
-#| label: fig-ppcheckandposteriorvsprior
+#| label: fig-referred_informed_model_ppcheckandposteriorvsprior
 #| layout-ncol: 2
@@
 #| label: fig-total_coded_model_stanareyouokay
-#| fig-cap: "Checking the convergence of the MCMC algorithm"
+#| fig-cap: "Checking the convergence of the MCMC algorithm for total_coded_model"
 #| fig-subcap: ["Trace plot", "Rhat plot"]
@@
 #| label: fig-referred_informed_model_stanareyouokay
-#| fig-cap: "Checking the convergence of the MCMC algorithm"
+#| fig-cap: "Checking the convergence of the MCMC algorithm for referred_informed_model"
 #| fig-subcap: ["Trace plot", "Rhat plot"]

### 2024-03-12 scripts/04-model.R
updated model to poisson

@@ -24,7 +24,7 @@ total_coded_model <-
   stan_glm(
     formula = Death_Count ~ Total_Coded,
     data = cleaned_data,
-    family = gaussian(),
+    family = poisson(link = "log"),
     prior = normal(location = 0, scale = 2.5, autoscale = TRUE),
     prior_intercept = normal(location = 0, scale = 2.5, autoscale = TRUE),
     prior_aux = exponential(rate = 1, autoscale = TRUE),
@@ -36,7 +36,7 @@ referred_informed_model <-
   stan_glm(
     formula = Death_Count ~ Referred + Informed,
     data = cleaned_data,
-    family = gaussian(),
+    family = poisson(link = "log"),
     prior = normal(location = 0, scale = 2.5, autoscale = TRUE),
     prior_intercept = normal(location = 0, scale = 2.5, autoscale = TRUE),
     prior_aux = exponential(rate = 1, autoscale = TRUE),

### 2024-03-12 paper/paper.qmd
changed modelsummary and apendix
changed apendix and modelsummary

@@
 
-$y_i|\mu_i$, $\sigma \sim \mbox{Normal}(\mu_i, \sigma)$
+$y_i|\lambda_i$, $\sigma \sim \mbox{Poisson}(\lambda_i)$
 
-$\mu_i = \alpha + \phi_i$
+$lambda_i = \alpha + \phi_i$
 
@@
 
-$y_i|\mu_i$, $\sigma \sim \mbox{Normal}(\mu_i, \sigma)$
+$y_i|\mu_i$, $\sigma \sim \mbox{Poisson}(\lambda_i)$
 
-$\mu_i = \alpha + \beta_i + \gamma_i$
+$\lambda_i = \alpha + \beta_i + \gamma_i$
 
@@
 
-We expect a net negative relationship between the net efforts made by the helpline staff (Recorded by the Total_Coded column) and homeless death count, which implies that net effect of helpline calls **reduces** homeless death count in Toronto.
+We expect a net negative relationship between the net efforts made by the helpline staff (Recorded by the Total_Coded) and homeless death count, which implies that net effect of helpline calls **reduces** homeless death count in Toronto.
 
@@
   statistic = "mad",
-  fmt = 3
+  fmt = 4
 )

### 2024-03-12 paper/paper.qmd
changed generalized model back to gaussian

@@
   - Sandy Yu
-thanks: "Code and data are available at: LINK."
+thanks: "Code and data are available at: https://github.com/Jingying-yu/help-line-homeless-death-analysis.git"
 date: today
@@
 
-$y_i|\lambda_i$, $\sigma \sim \mbox{Poisson}(\lambda_i)$
+$y_i|\mu_i$, $\sigma \sim \mbox{Normal}(\mu_i, \sigma)$
 
-$lambda_i = \alpha + \phi_i$
+$mu_i = \alpha + \phi_i$
 
@@
 
-$y_i|\mu_i$, $\sigma \sim \mbox{Poisson}(\lambda_i)$
+$y_i|\mu_i$, $\sigma \sim \mbox{Normal}(\mu_i, \sigma)$
 
-$\lambda_i = \alpha + \beta_i + \gamma_i$
+$\mu_i = \alpha + \beta_i + \gamma_i$
 
@@
 ```{r}
+#| label: fig-total_coded
+#| fig-cap: Visualization to show correlation between number of Calls Coded (represented by the red line) and Homeless Death Counts (represented by the blue line)
 #| echo: false
-#| eval: true
-#| label: tbl-total_coded_modelresults
-#| tbl-cap: "Explanatory model of homeless death count in relation to total number of helpline calls coded per month"
-#| warning: false
+#| message: false
 
-modelsummary::modelsummary(
-  list(
-    "Total Coded Model" = total_coded_model
-  ),
-  statistic = "mad",
-  fmt = 4
-)
+cleaned_data |> ggplot(aes(x = Total_Coded, y = Death_Count)) + geom_point(alpha = 0.5) + 
+  geom_smooth(method = "lm", se = TRUE, color = "blue", linetype = "dashed", formula = "y ~ x") +
+  labs(x = "Monthly Number of Calls Coded (per month)", y = "Monthly Number of Homeless Deaths")
 ```
@@
 #| eval: true
-#| label: tbl-referred_informed_modelresults
-#| tbl-cap: "Explanatory model of homeless death count in relation to the number of homeless referred to shelters and provided with information on homelessness prevention per month"
+#| label: tbl-modelresults
+#| tbl-cap: "Explanatory model of homeless death count in relation to different helpline efforts"
+#| tbl-subcap: "statistical significances are indicated by p < 0.1 *, p < 0.05 **, p < 0.01 ***, p < 0.001"
 #| warning: false
@@
   list(
-    "Referred and Informed Model" = referred_informed_model
+    "Total Coded Model" = total_coded_model, "Referred and Informed Model" = referred_informed_model
   ),
   statistic = "mad",
+  stars = TRUE,
   fmt = 4

### 2024-03-12 scripts/04-model.R

@@ -24,7 +24,7 @@ total_coded_model <-
   stan_glm(
     formula = Death_Count ~ Total_Coded,
     data = cleaned_data,
-    family = poisson(link = "log"),
+    family = gaussian(),
     prior = normal(location = 0, scale = 2.5, autoscale = TRUE),
     prior_intercept = normal(location = 0, scale = 2.5, autoscale = TRUE),
     prior_aux = exponential(rate = 1, autoscale = TRUE),
@@ -36,7 +36,7 @@ referred_informed_model <-
   stan_glm(
     formula = Death_Count ~ Referred + Informed,
     data = cleaned_data,
-    family = poisson(link = "log"),
+    family = gaussian(),
     prior = normal(location = 0, scale = 2.5, autoscale = TRUE),
     prior_intercept = normal(location = 0, scale = 2.5, autoscale = TRUE),
     prior_aux = exponential(rate = 1, autoscale = TRUE),

### 2024-03-12 paper/paper.qmd
written abstract for paper

@@
 date-format: long
-abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
+abstract: "This paper analyzes the influence of Central Intake Line staff efforts on the reduction of homeless death count in Toronto.
+Data on coded number of calls from Central Intake Call Wrap-Up Codes dataset and data on monthly homeless death count from Deaths of People Experiencing Homelessness dataset are used in generalized linear regression models to estimate the influence.
+We find that the staffs’ net efforts create a statistically insignificant influence on the reduction of homeless death, with specific types of efforts appearing counterproductive.
+This implies that, while a positive influence does exist, the impact of the Central Intake Line staff is unfortunately minimal from a statistical point of view."
 format: pdf

### 2024-03-12 paper/paper.qmd
finished draft up to result

@@
 We find that the staffs’ net efforts create a statistically insignificant influence on the reduction of homeless death, with specific types of efforts appearing counterproductive.
-This implies that, while a positive influence does exist, the impact of the Central Intake Line staff is unfortunately minimal from a statistical point of view."
+This implies that while a positive influence does exist, from a statistical point of view, the impact of the Central Intake Line staff is not significantly different from non-existent."
 format: pdf
@@
 
-You can and should cross-reference sections and sub-sections. We use @citeR and @rohan.
+The City of Toronto has been consistently providing funding and staff in an effort to reduce the active homeless population within its governing district.
+Amongst numerous city efforts, the 24/7 helpline — Toronto Central Intake Line — was created to offer referrals to emergency shelters, sleeping accommodations, and provide general information about homelessness and prevention.
+[@Central_Intake_Call].
+Starting in 2020, detailed data about the Central Intake Line became available on the OpenDataToronto portal [@OpenDataToronto].
+
+The estimand of the paper focuses on examining the influence of helpline efforts on the reduction of homeless deaths in Toronto. 
+Using Central Intake Call Wrap-up Codes data [@Central_Intake_Call] from OpenDataToronto [@OpenDataToronto], three different aspects of the helpline efforts were isolated: total calls coded, referral to shelter, and homelessness prevention information provided.
+These three key aspects were measured against the monthly cumulative death count from Deaths of People Experiencing Homelessness Data [@Homeless_Death_Count] documented by the Toronto Public Health [@TPH].
+The analyses yielded an insignificant negative correlation between the net efforts of the helpline staff.
+The variable referral to shelter yields a positive correlation with homeless death count, whereas the effort to provide homelessness information yields a negative correlation.
+This implies that the net influence of helpline efforts is statistically negligible, while individual efforts can be productive or counterproductive.
+This examination in the net efforts and individual efforts can provide the helpline with a suggestion of which types of services or calls would be more economically efficient to allocate their labor resources on.
 
@@
 
-The goal of our modelling strategy is twofold. Firstly,...
+While we can still make claims on the correlations between helpline efforts and homeless death count without modelling, regression analysis is still necessary to provide rigorous backbones for a claim's statistical significance.
 
@@
 Magnitude of effect created by the helpline efforts can be estimated through linear models.
+Gaussian regression model is best suited for our analytical purposes.
+Other generalized linear models such as Logistic and Multilevel are not considered due to the nature of the variables in interest.
+Logistic regression model requires data that yields either an **yes** or **no** result, whereas multilevel model require more complexity between variables.
+Due to the nature of the Poisson function, the Poisson model was considered and discarded because model results in extremely small values with no evidently different interpretations.
 
@@
 
-Additionally, we expect a negative relationship between homeless death and the number of homeless individuals referred to shelter & the number of individuals provided with homelessness prevention information.
+Additionally, we expect a negative relationship between homeless death and the two individual efforts: *number of homeless individuals referred to shelter*, and *number of individuals provided with homelessness prevention information*.
 Since both factors are coded efforts made by the helpline, both factors should also help to reduce homeless death count in Toronto.
@@
 #| label: fig-total_coded
-#| fig-cap: Visualization to show correlation between number of Calls Coded (represented by the red line) and Homeless Death Counts (represented by the blue line)
+#| fig-cap: Visualization to show correlation between number of Calls Coded and Homeless Death Counts
 #| echo: false
@@
 ## First discussion point {#sec-first-point}
-
-If my paper were 10 pages, then should be be at least 2.5 pages. The discussion is a chance to show off what you know and what you learnt from all this.
 

### 2024-03-12 paper/paper.qmd
fixed a few typos, still can't render. unknown error

@@
 ---
-title: "My title"
-subtitle: "My subtitle if needed"
+title: "Minimal Positive Influence of Helpline Efforts on Reduction of Homeless Death in Toronto"
 author: 
@@
 bibliography: references.bib
+editor: 
+  markdown: 
+    wrap: 72
 ---
@@
 library(tidyverse)
+library(readr)
 library(rstanarm)
-library(arrow)
 library(knitr)
@@
 
-The City of Toronto has been consistently providing funding and staff in an effort to reduce the active homeless population within its governing district.
-Amongst numerous city efforts, the 24/7 helpline — Toronto Central Intake Line — was created to offer referrals to emergency shelters, sleeping accommodations, and provide general information about homelessness and prevention.
-[@Central_Intake_Call].
-Starting in 2020, detailed data about the Central Intake Line became available on the OpenDataToronto portal [@OpenDataToronto].
+The City of Toronto has been consistently providing funding and staff in
+an effort to reduce the active homeless population within its governing
+district. Amongst numerous city efforts, the 24/7 helpline — Toronto
+Central Intake Line — was created to offer referrals to emergency
+shelters, sleeping accommodations, and provide general information about
+homelessness and prevention. [@Central_Intake_Call]. Starting in 2020,
+detailed data about the Central Intake Line became available on the
+OpenDataToronto portal [@OpenDataToronto].
 
-The estimand of the paper focuses on examining the influence of helpline efforts on the reduction of homeless deaths in Toronto. 
-Using Central Intake Call Wrap-up Codes data [@Central_Intake_Call] from OpenDataToronto [@OpenDataToronto], three different aspects of the helpline efforts were isolated: total calls coded, referral to shelter, and homelessness prevention information provided.
-These three key aspects were measured against the monthly cumulative death count from Deaths of People Experiencing Homelessness Data [@Homeless_Death_Count] documented by the Toronto Public Health [@TPH].
-The analyses yielded an insignificant negative correlation between the net efforts of the helpline staff.
-The variable referral to shelter yields a positive correlation with homeless death count, whereas the effort to provide homelessness information yields a negative correlation.
-This implies that the net influence of helpline efforts is statistically negligible, while individual efforts can be productive or counterproductive.
-This examination in the net efforts and individual efforts can provide the helpline with a suggestion of which types of services or calls would be more economically efficient to allocate their labor resources on.
+The estimand of the paper focuses on examining the influence of helpline
+efforts on the reduction of homeless deaths in Toronto. Using Central
+Intake Call Wrap-up Codes data [@Central_Intake_Call] from
+OpenDataToronto [@OpenDataToronto], three different aspects of the
+helpline efforts were isolated: total calls coded, referral to shelter,
+and homelessness prevention information provided. These three key
+aspects were measured against the monthly cumulative death count from
+Deaths of People Experiencing Homelessness Data [@Homeless_Death_Count]
+documented by the Toronto Public Health [@TPH]. The analyses yielded an
+insignificant negative correlation between the net efforts of the
+helpline staff. The variable referral to shelter yields a positive
+correlation with homeless death count, whereas the effort to provide
+homelessness information yields a negative correlation. This implies
+that the net influence of helpline efforts is statistically negligible,
+while individual efforts can be productive or counterproductive. This
+examination in the net efforts and individual efforts can provide the
+helpline with a suggestion of which types of services or calls would be
+more economically efficient to allocate their labor resources on.
 
-Analyses and findings in this paper are structured into several sections: @sec-data -- Data, @sec-model – Model, @sec-results -- Results, and @sec-discussion -- Discussion.
-The Data section examines all datasets and variables kept for analysis, followed by an explanation of their data cleaning processes.
-The Model section defines linear models used for further analysis, explain its components, and presents model justifications.
-The Result section focuses on visualizing and presenting the model results through data presented in Data section.
-The Discussion section further evaluate the interpretations behind the model results presented in the previous section, and touches on any weaknesses and next steps.
+Analyses and findings in this paper are structured into several
+sections: @sec-data -- Data, @sec-model – Model, @sec-results --
+Results, and @sec-discussion -- Discussion. The Data section examines
+all datasets and variables kept for analysis, followed by an explanation
+of their data cleaning processes. The Model section defines linear
+models used for further analysis, explain its components, and presents
+model justifications. The Result section focuses on visualizing and
+presenting the model results through data presented in Data section. The
+Discussion section further evaluate the interpretations behind the model
+results presented in the previous section, and touches on any weaknesses
+and next steps.
 
@@
 
-All data used in this paper are obtained through OpenDataToronto Portal [@OpenDataToronto].
-Two different datasets: Central Intake Call Wrap-Up Codes Data [@Central_Intake_Call] and Deaths of People Experiencing Homelessness[@Homeless_Death_Count], are retrieved to analyze the effect of Toronto’s Central Call Line (denoted as *Helpline* for the remainder of this paper) efforts to the death counts of homeless individuals in Toronto.
-Data is cleaned and analyzed using the open source statistical programming language R [@citeR] and supporting packages tidyverse [@tidyverse], janitor [@janitor], dplyr [@dplyr], rstanarm [@rstanarm], arrow [@arrow], ggplot2 [@ggplot2], and knitr [@knitr].
-Detailed description of each dataset can be found in the subsections below.
+All data used in this paper are obtained through OpenDataToronto Portal
+[@OpenDataToronto]. Two different datasets: Central Intake Call Wrap-Up
+Codes Data [@Central_Intake_Call] and Deaths of People Experiencing
+Homelessness[@Homeless_Death_Count], are retrieved to analyze the effect
+of Toronto’s Central Call Line (denoted as *Helpline* for the remainder
+of this paper) efforts to the death counts of homeless individuals in
+Toronto. Data is cleaned and analyzed using the open source statistical
+programming language R [@citeR] and supporting packages tidyverse
+[@tidyverse], janitor [@janitor], rstanarm [@rstanarm], arrow [@arrow],
+ggplot2 [@ggplot2], and knitr [@knitr]. Detailed description of each
+dataset can be found in the subsections below.
 
@@
 
-On the OpenDataToronto portal, there are several datasets that reflect the City’s effort to shelter the local homeless population.
-The Central Intake Call Wrap-Up Codes Dataset [@Central_Intake_Call], stored in the Central Intake Calls Catalogue [@Central_Intake_Call], is one of the freshest and most detailed.
-Data is stored and published by the Shelter, Support & Housing Administration since November of 2020 and refreshes on a monthly basis.
-The latest refresh occurred on January 15th, 2024.
+On the OpenDataToronto portal, there are several datasets that reflect
+the City’s effort to shelter the local homeless population. The Central
+Intake Call Wrap-Up Codes Dataset [@Central_Intake_Call], stored in the
+Central Intake Calls Catalogue [@Central_Intake_Call], is one of the
+freshest and most detailed. Data is stored and published by the Shelter,
+Support & Housing Administration since November of 2020 and refreshes on
+a monthly basis. The latest refresh occurred on January 15th, 2024.
 
-The data set provides a daily summary of the number of calls received, the number of calls classified into distinct wrap-up codes by the nature of its issue, and a count of calls under each wrap-up code.
-One of the example wrap-up codes in the original data set was: *Code 1A - Referral to a Sleeping/Resting Space*.
-The original data set includes 13 distinct wrap-up codes; only two codes, *Code 1A — Referral to a Sleeping/Resting Space* and *Code 2C — Information - Homelessness & Prevention Services*, were chosen for our analysis.
-Code 1A and Code 2C are best suited as measurements for positive impact the Central Intake Line could provide because they provide a count of the number of callers provided with directions or advice.
-Other non-suitable wrap-up codes include: *Code 1D - Declined Shelter/Resting Space*, *Code 4B - Disconnected - No Outcome*, etc.
+The data set provides a daily summary of the number of calls received,
+the number of calls classified into distinct wrap-up codes by the nature
+of its issue, and a count of calls under each wrap-up code. One of the
+example wrap-up codes in the original data set was: *Code 1A - Referral
+to a Sleeping/Resting Space*. The original data set includes 13 distinct
+wrap-up codes; only two codes, *Code 1A — Referral to a Sleeping/Resting
+Space* and *Code 2C — Information - Homelessness & Prevention Services*,
+were chosen for our analysis. Code 1A and Code 2C are best suited as
+measurements for positive impact the Central Intake Line could provide
+because they provide a count of the number of callers provided with
+directions or advice. Other non-suitable wrap-up codes include: *Code
+1D - Declined Shelter/Resting Space*, *Code 4B - Disconnected - No
+Outcome*, etc.
 
-The final dataset only includes monthly cumulative data before July of 2023. The rationalization behind the action will be explained in @sec-combined-data.
+The final dataset only includes monthly cumulative data before July of
+2023. The rationalization behind the action will be explained in
+@sec-combined-data.
 
@@
 #| echo: false
+#| warning: false
 
-cleaned_data <- read_parquet(here::here("data/analysis_data/cleaned_data.parquet"))
+cleaned_data <- read_csv(here::here("data/analysis_data/cleaned_data.csv"))
 
@@
 
-The Deaths of People Experiencing Homelessness Dataset [@Homeless_Death_Count] contains monthly cumulative records of homeless deaths.
-The dataset is published by Toronto Public Health [@TPH].
-The earliest data record started in January of 2017, and the latest record ends in June of 2023.
+The Deaths of People Experiencing Homelessness Dataset
+[@Homeless_Death_Count] contains monthly cumulative records of homeless
+deaths. The dataset is published by Toronto Public Health [@TPH]. The
+earliest data record started in January of 2017, and the latest record
+ends in June of 2023.
 
-The original dataset contains three columns: *Year of death*, *Month of death*, and *Count*.
-After careful inspection of raw data, any rows that containing an “unknown” value are excluded.
-Although this action created a source of error in future analyses, this is still a necessary step because we are plotting death counts against a timeline.
+The original dataset contains three columns: *Year of death*, *Month of
+death*, and *Count*. After careful inspection of raw data, any rows that
+containing an “unknown” value are excluded. Although this action created
+a source of error in future analyses, this is still a necessary step
+because we are plotting death counts against a timeline.
 
-Final dataset only includes data from November 2020 to June 2023 (@tbl-death-count). The rationalization behind the action will be explained in @sec-data-diff-datasets.
+Final dataset only includes data from November 2020 to June 2023
+(@tbl-death-count). The rationalization behind the action will be
+explained in @sec-data-diff-datasets.
 
@@
 
-During the data cleaning process, code was written to ensure that both the Central Intake Call Wrap-Up Codes Dataset [@Central_Intake_Call] and the Deaths of People Experiencing Homelessness Dataset [@Homeless_Death_Count] are filtered to include only data between 1st November, 2020 to 30st June, 2023.
+During the data cleaning process, code was written to ensure that both
+the Central Intake Call Wrap-Up Codes Dataset [@Central_Intake_Call] and
+the Deaths of People Experiencing Homelessness Dataset
+[@Homeless_Death_Count] are filtered to include only data between 1st
+November, 2020 to 30st June, 2023.
 
-The decision is reached by taking the common time period between the two datasets.
-In the latest refresh, the Central Intake Call Wrap-Up Codes Dataset [@Central_Intake_Call] begins on 3rd November, 2020 and end on 31st December, 2023; whereas the Deaths of People Experiencing Homelessness Dataset [@Homeless_Death_Count] begins on January of 2017 and ends on June 2023.
+The decision is reached by taking the common time period between the two
+datasets. In the latest refresh, the Central Intake Call Wrap-Up Codes
+Dataset [@Central_Intake_Call] begins on 3rd November, 2020 and end on
+31st December, 2023; whereas the Deaths of People Experiencing
+Homelessness Dataset [@Homeless_Death_Count] begins on January of 2017
+and ends on June 2023.
 
-The ultimate purpose of taking the common time period is to ensure that we can have the same amount of observations for analysis.
-Thus a combined dataset that kept the variables of interest in both datasets is created (@tbl-combined).
+The ultimate purpose of taking the common time period is to ensure that
+we can have the same amount of observations for analysis. Thus a
+combined dataset that kept the variables of interest in both datasets is
+created (@tbl-combined).
 
@@
 
-While we can still make claims on the correlations between helpline efforts and homeless death count without modelling, regression analysis is still necessary to provide rigorous backbones for a claim's statistical significance.
+While we can still make claims on the correlations between helpline
+efforts and homeless death count without modelling, regression analysis
+is still necessary to provide rigorous backbones for a claim's
+statistical significance.
 
-Here we briefly describe the Bayesian analysis model used to investigate the correlation between homeless death counts in Toronto and the efforts of the Helpline staff.
-Background details and diagnostics are included in [Appendix -@sec-model-details].
+Here we briefly describe the Bayesian analysis model used to investigate
+the correlation between homeless death counts in Toronto and the efforts
+of the Helpline staff. Background details and diagnostics are included
+in [Appendix -@sec-model-details].
 
@@
 
-Magnitude of effect created by the helpline efforts can be estimated through linear models.
-Gaussian regression model is best suited for our analytical purposes.
-Other generalized linear models such as Logistic and Multilevel are not considered due to the nature of the variables in interest.
-Logistic regression model requires data that yields either an **yes** or **no** result, whereas multilevel model require more complexity between variables.
-Due to the nature of the Poisson function, the Poisson model was considered and discarded because model results in extremely small values with no evidently different interpretations.
+Magnitude of effect created by the helpline efforts can be estimated
+through linear models. Gaussian regression model is best suited for our
+analytical purposes. Other generalized linear models such as Logistic
+and Multilevel are not considered due to the nature of the variables in
+interest. Logistic regression model requires data that yields either an
+**yes** or **no** result, whereas multilevel model require more
+complexity between variables. Due to the nature of the Poisson function,
+the Poisson model was considered and discarded because model results in
+extremely small values with no evidently different interpretations.
 
@@
 
-$mu_i = \alpha + \phi_i$
+$\mu_i = \alpha + \phi_i$
 
@@
 
--   $y_i$ is the number of homeless death count in Toronto recorded by @TPH per month
+-   $y_i$ is the number of homeless death count in Toronto recorded by
+    @TPH per month
 
--   $\phi_i$ is the total number of calls received and coded by the helpline per month
+-   $\phi_i$ is the total number of calls received and coded by the
+    helpline per month
 
@@
 
--   $y_i$ is the number of homeless death count in Toronto recorded by @TPH per month
+-   $y_i$ is the number of homeless death count in Toronto recorded by
+    @TPH per month
 
--   $\beta_i$ is the number of homeless individuals referred to shelters through the helpline, per month
+-   $\beta_i$ is the number of homeless individuals referred to shelters
+    through the helpline, per month
 
--   $\gamma_i$ is the number of individuals provided with information on homelessness prevention through the helpline, per month
+-   $\gamma_i$ is the number of individuals provided with information on
+    homelessness prevention through the helpline, per month
 
-We run the model in R [@citeR] using the `rstanarm` package of @rstanarm. We use the default priors from `rstanarm`.
+We run the model in R [@citeR] using the `rstanarm` package of
+@rstanarm. We use the default priors from `rstanarm`.
 
@@
 
-We expect a net negative relationship between the net efforts made by the helpline staff (Recorded by the Total_Coded) and homeless death count, which implies that net effect of helpline calls **reduces** homeless death count in Toronto.
+We expect a net negative relationship between the net efforts made by
+the helpline staff (Recorded by the Total_Coded) and homeless death
+count, which implies that net effect of helpline calls **reduces**
+homeless death count in Toronto.
 
-Additionally, we expect a negative relationship between homeless death and the two individual efforts: *number of homeless individuals referred to shelter*, and *number of individuals provided with homelessness prevention information*.
-Since both factors are coded efforts made by the helpline, both factors should also help to reduce homeless death count in Toronto.
+Additionally, we expect a negative relationship between homeless death
+and the two individual efforts: *number of homeless individuals referred
+to shelter*, and *number of individuals provided with homelessness
+prevention information*. Since both factors are coded efforts made by
+the helpline, both factors should also help to reduce homeless death
+count in Toronto.
 
@@
 
-Our results are summarized in @tbl-total_coded_modelresults and @tbl-referred_informed_modelresults.
+Our results are summarized in @tbl-total_coded_modelresults and
+@tbl-referred_informed_modelresults.
 
@@
 
+-   there exist a net negative correlation between helpline efforts and
+    homeless death count in Toronto
+
 ```{r}
-#| label: fig-total_coded
+#| label: fig-total-coded
 #| fig-cap: Visualization to show correlation between number of Calls Coded and Homeless Death Counts
@@
 
+Hypothesis 1: - null hypothesis: true effect of total_calls_coded = 0 -
+use t-stat to check at 95% significance level
+
+Hypothesis 2: - null hypothesis: true effect of referred = 0 - use
+t-stat to check at 95% significance level
+
+Hypothesis 3: - null hypothesis: true effect of referred = 0 - use
+t-stat to check at 95% significance level
+
 # Discussion {#sec-discussion}
 
-## First discussion point {#sec-first-point}
+## Realistic Interpretation of Net Efforts
 
-## Second discussion point
+-   On average, for every increase in calls coded by the helpline, there
+    is a 0.0003 unit decrease in homeless death in Toronto. There is an
+    overall reduction, albeit very small, in homeless death as the
+    number of total coded calls increase. This implies that the helpline
+    need to take at minimum 3333 calls per month to save 1 homeless life
+    in Toronto. On average, the helpline takes 14828.59 calls per month,
+    meaning that 4.45 lives are saved on average.
+-   4.45 is not a significant number in both a practical and statistical
+    sense. To improve the return on total number of calls coded, we
+    attempted to identify promising call codes that contribute to the
+    net positive reduction in homeless death. Out of the 13 different
+    call codes, *Referral to Shelter* and *Information on Homeless
+    Prevention* are best suited as individual efforts of measurement for
+    positive impacts because they provide a count of the number of
+    callers provided with directions or advice.
 
-## Third discussion point
+## Individual Effort: Referral to Shelter
+
+-   On average, for every homeless caller referred to shelter, there is
+    a 0.0059 unit **increase** in homeless death in Toronto. Though not
+    significant on a statistical level, this trend is still very
+    counter-intuitive discouraging. In the case where the correlation is
+    more significant, we would want to further analyze factor related to
+    referrals to shelter. Accuracy on the current status of shelters,
+    level of detail on instructed, and misjudgment of shelter
+    eligibility are possible factors of examination. However, since the
+    effect of this call code is statistically insignificant, it is more
+    likely just a fluke caused by the dataset.
+
+## Individual Effort: Information on Homelessness Prevention
 
@@
 
-Weaknesses and next steps should also be included.
+Weaknesses: very small sample size, only 32 observations Next steps:
+investigate into the possible factors that caused a net zero impact on
+reduction of homeless death count and propose possible solution using
+data.
 
@@
 
-In @fig-total_coded_model_ppcheckandposteriorvsprior-1 we implement a posterior predictive check. This shows...
+In @fig-total-coded-model-ppcheckandposteriorvsprior-1 we implement a
+posterior predictive check. This shows...
 
-In @fig-total_coded_model_ppcheckandposteriorvsprior-2 we compare the posterior with the prior. This shows...
+In @fig-total-coded-model-ppcheckandposteriorvsprior-2 we compare the
+posterior with the prior. This shows...
 
@@
 #| warning: false
-#| label: fig-total_coded_model_ppcheckandposteriorvsprior
+#| label: fig-total-coded-model-ppcheckandposteriorvsprior
 #| layout-ncol: 2
@@
 
-In @fig-referred_informed_model_ppcheckandposteriorvsprior-1 we implement a posterior predictive check. This shows...
+In @fig-referred-informed-model-ppcheckandposteriorvsprior-1 we
+implement a posterior predictive check. This shows...
 
-In @fig-referred_informed_model_ppcheckandposteriorvsprior-2 we compare the posterior with the prior. This shows...
+In @fig-referred-informed-model-ppcheckandposteriorvsprior-2 we compare
+the posterior with the prior. This shows...
 
@@
 #| warning: false
-#| label: fig-referred_informed_model_ppcheckandposteriorvsprior
+#| label: fig-referred-informed-model-ppcheckandposteriorvsprior
 #| layout-ncol: 2
@@
 
-@fig-total_coded_model_stanareyouokay-1 is a trace plot. It shows... This suggests...
+@fig-total-coded-model-stanareyouokay-1 is a trace plot. It shows...
+This suggests...
 
-@fig-total_coded_model_stanareyouokay-2 is a Rhat plot. It shows... This suggests...
+@fig-total-coded-model-stanareyouokay-2 is a Rhat plot. It shows... This
+suggests...
 
@@
 #| warning: false
-#| label: fig-total_coded_model_stanareyouokay
+#| label: fig-total-coded-model-stanareyouokay
 #| fig-cap: "Checking the convergence of the MCMC algorithm for total_coded_model"
@@
 
-@fig-referred_informed_model_stanareyouokay-1 is a trace plot. It shows... This suggests...
+@fig-referred-informed-model-stanareyouokay-1 is a trace plot. It
+shows... This suggests...
 
-@fig-referred_informed_model_stanareyouokay-2 is a Rhat plot. It shows... This suggests...
+@fig-referred-informed-model-stanareyouokay-2 is a Rhat plot. It
+shows... This suggests...
 
@@
 #| warning: false
-#| label: fig-referred_informed_model_stanareyouokay
+#| label: fig-referred-informed-model-stanareyouokay
 #| fig-cap: "Checking the convergence of the MCMC algorithm for referred_informed_model"

### 2024-03-12 paper/paper.qmd
found the error code chunk, it's the modelsummary chunk

@@
 library(knitr)
+library(modelsummary)
 library(ggplot2)
@@
 
-Our results are summarized in @tbl-total_coded_modelresults and
-@tbl-referred_informed_modelresults.
+Our results are summarized in @tbl-modelresults.
 
@@
 #| tbl-subcap: "statistical significances are indicated by p < 0.1 *, p < 0.05 **, p < 0.01 ***, p < 0.001"
-#| warning: false
 
-modelsummary::modelsummary(
+modelsummary(
   list(
@@
   stars = TRUE,
-  fmt = 4
+  fmt = 4,
+  metrics = c("RMSE", "R2")
 )

### 2024-03-12 paper/paper.qmd
rendering issue has been fixed after deleting tbl-subcap

@@
 #| tbl-cap: "Explanatory model of homeless death count in relation to different helpline efforts"
-#| tbl-subcap: "statistical significances are indicated by p < 0.1 *, p < 0.05 **, p < 0.01 ***, p < 0.001"
 

### 2024-03-12 paper/paper.qmd
Edited the result section

@@
 
--   there exist a net negative correlation between helpline efforts and
-    homeless death count in Toronto
+-   Under the Gaussian regression model, @fig-total-coded illustrates a
+    fitted line that estimates the linear relationship between the
+    number of total calls coded and homeless death count in Toronto. The
+    graph suggest that there exist a net negative correlation between
+    the two variable. According to the graph, homeless death count
+    decrease as total number of calls coded increase. The significance
+    of this relationship is discussed below in in the model summary
+    table.
 
@@
 ```
+
+-   The model summary table, @tbl-modelresults, displays the coefficient
+    values of the predictor variables against response variable:
+    homeless death count in Toronto. Coefficients of predictors indicate
+    their influence against the response variable. For example, the
+    column on the left shows that, under Model 1, every 1 additional
+    helpline call coded and decrease the homeless death count by 0.0003.
+    The ***+p \<...*** section at the bottom of the table represents
+    statistically significance of the coefficient values. As indicated
+    by the ***+p\<...*** legend, the coefficients with 1 \*, coefficient
+    is significant at 95% confidence level; for \*\*, coefficient is
+    significant at 99% confidence level, and so on. However, as we can
+    see from the table below, no \* exists for the coefficients in both
+    models.
 
@@
 ```
-
-Hypothesis 1: - null hypothesis: true effect of total_calls_coded = 0 -
-use t-stat to check at 95% significance level
-
-Hypothesis 2: - null hypothesis: true effect of referred = 0 - use
-t-stat to check at 95% significance level
-
-Hypothesis 3: - null hypothesis: true effect of referred = 0 - use
-t-stat to check at 95% significance level
 

### 2024-03-12 paper/paper.qmd
Added rationalization of existence for model 2 in model section
Added material to result and discussion section

@@
 #| echo: false
-#| warning: false
+#| message: false
 
@@
 
+The Total Coded model estimates the the total helpline efforts against
+Toronto's homeless death count.
+
 $y_i|\mu_i$, $\sigma \sim \mbox{Normal}(\mu_i, \sigma)$
@@
 ### Model 2: Referred Informed Model
+
+In case of oversimplification, a second model is proposed to isolate the
+effects of calls that refer individuals to shelter and calls that
+provide information on homelessness prevention.
 
@@
 
-## Realistic Interpretation of Net Efforts
+## Interpretation of Efforts
 
@@
     callers provided with directions or advice.
-
-## Individual Effort: Referral to Shelter
-
 -   On average, for every homeless caller referred to shelter, there is
@@
     eligibility are possible factors of examination. However, since the
-    effect of this call code is statistically insignificant, it is more
-    likely just a fluke caused by the dataset.
+    effect of this call code is statistically insignificant, it is also
+    likely to be just a fluke of observation.
+-   For every caller provided with information on homeless prevention
+    information, there is an average decrease of 0.0048 death count in
+    Toronto.
 
-## Individual Effort: Information on Homelessness Prevention
+## Implication of Insignificance: More Qeustions than Answers
+
+-   Homeless life is not easy, data shows that a total of 522 homeless
+    individual died in Toronto between November 2020 to June 2023.
+
+-   The Central Intake Line is created with the intend to help homeless
+    individuals in need. It provides a 24/7 platform for individuals to
+    receive government help.
+
+-   The insignificance of its influence suggests that the helpline has
+    not fulfilled its intended purpose, though it is also important to
+    note that having insignificant effect on reducing death count does
+    not mean the helpline has not contributed to the well-being of
+    Toronto's homeless population in other ways.
+
+-   This makes us question
 

### 2024-03-16 paper/paper.qmd
finished final touches, waiting for posit cloud to become available for rendering

@@
 (@tbl-death-count). The rationalization behind the action will be
-explained in @sec-data-diff-datasets.
+explained in @sec-combined-data.
 
@@
 
-$y_i|\mu_i$, $\sigma \sim \mbox{Normal}(\mu_i, \sigma)$
+$$y_i|\mu_i, \sigma \sim \mbox{Normal}(\mu_i, \sigma)$$
 
-$\mu_i = \alpha + \phi_i$
+$$\mu_i = \alpha + \phi_i$$
 
-$\alpha \sim \mbox{Normal}(0, 2.5)$
+$$\alpha \sim \mbox{Normal}(0, 2.5)$$
 
-$\phi \sim \mbox{Normal}(0, 2.5)$
+$$\phi \sim \mbox{Normal}(0, 2.5)$$
 
-$\sigma \sim \mbox{Exponential}(1)$
+$$\sigma \sim \mbox{Exponential}(1)$$
 
@@
 
-$y_i|\mu_i$, $\sigma \sim \mbox{Normal}(\mu_i, \sigma)$
+$$y_i|\mu_i, \sigma \sim \mbox{Normal}(\mu_i, \sigma)$$
 
-$\mu_i = \alpha + \beta_i + \gamma_i$
+$$\mu_i = \alpha + \beta_i + \gamma_i$$
 
-$\alpha \sim \mbox{Normal}(0, 2.5)$
+$$\alpha \sim \mbox{Normal}(0, 2.5)$$
 
-$\beta \sim \mbox{Normal}(0, 2.5)$
+$$\beta \sim \mbox{Normal}(0, 2.5)$$
 
-$\gamma \sim \mbox{Normal}(0, 2.5)$
+$$\gamma \sim \mbox{Normal}(0, 2.5)$$
 
-$\sigma \sim \mbox{Exponential}(1)$
+$$\sigma \sim \mbox{Exponential}(1)$$
 
@@
 
--   Under the Gaussian regression model, @fig-total-coded illustrates a
-    fitted line that estimates the linear relationship between the
-    number of total calls coded and homeless death count in Toronto. The
-    graph suggest that there exist a net negative correlation between
-    the two variable. According to the graph, homeless death count
-    decrease as total number of calls coded increase. The significance
-    of this relationship is discussed below in in the model summary
-    table.
+Under the Gaussian regression model, @fig-total-coded illustrates a
+fitted line that estimates the linear relationship between the number of
+total calls coded and homeless death count in Toronto. The graph suggest
+that there exist a net negative correlation between the two variable.
+According to the graph, homeless death count decrease as total number of
+calls coded increase. The significance of this relationship is discussed
+below in in the model summary table.
 
@@
 
--   The model summary table, @tbl-modelresults, displays the coefficient
-    values of the predictor variables against response variable:
-    homeless death count in Toronto. Coefficients of predictors indicate
-    their influence against the response variable. For example, the
-    column on the left shows that, under Model 1, every 1 additional
-    helpline call coded and decrease the homeless death count by 0.0003.
-    The ***+p \<...*** section at the bottom of the table represents
-    statistically significance of the coefficient values. As indicated
-    by the ***+p\<...*** legend, the coefficients with 1 \*, coefficient
-    is significant at 95% confidence level; for \*\*, coefficient is
-    significant at 99% confidence level, and so on. However, as we can
-    see from the table below, no \* exists for the coefficients in both
-    models.
+The model summary table, @tbl-modelresults, displays the coefficient
+values of the predictor variables against response variable: homeless
+death count in Toronto. Coefficients of predictors indicate their
+influence against the response variable. For example, the column on the
+left shows that, under Model 1, every 1 additional helpline call coded
+and decrease the homeless death count by 0.0003. The ***+p \<...***
+section at the bottom of the table represents statistically significance
+of the coefficient values. As indicated by the ***+p\<...*** legend, the
+coefficients with 1 \*, coefficient is significant at 95% confidence
+level; for \*\*, coefficient is significant at 99% confidence level, and
+so on. However, as we can see from the table below, no \* exists for the
+coefficients in both models.
 
@@
     positive impacts because they provide a count of the number of
-    callers provided with directions or advice.
--   On average, for every homeless caller referred to shelter, there is
-    a 0.0059 unit **increase** in homeless death in Toronto. Though not
-    significant on a statistical level, this trend is still very
-    counter-intuitive discouraging. In the case where the correlation is
-    more significant, we would want to further analyze factor related to
-    referrals to shelter. Accuracy on the current status of shelters,
-    level of detail on instructed, and misjudgment of shelter
-    eligibility are possible factors of examination. However, since the
-    effect of this call code is statistically insignificant, it is also
-    likely to be just a fluke of observation.
--   For every caller provided with information on homeless prevention
-    information, there is an average decrease of 0.0048 death count in
-    Toronto.
+    callers provided with directions or advice. For every caller
+    provided with information on homeless prevention information, there
+    is an average decrease of 0.0048 death count in Toronto. On the
+    other hand, for every homeless caller referred to shelter, there is
+    a 0.0059 unit of average **increase** in homeless death in Toronto.
+    This trend is very counter-intuitive and discouraging at first
+    glance. In the case where the correlation is more significant, we
+    would want to further analyze factor related to referrals to
+    shelter. Accuracy on the current status of shelters, level of detail
+    on instructed, and misjudgment of shelter eligibility are possible
+    factors of examination. However, since the effect of this call code
+    is statistically insignificant, it is also likely to be just a fluke
+    of observation.
 
-## Implication of Insignificance: More Qeustions than Answers
+## Factors Contributing to Insignificance
 
--   Homeless life is not easy, data shows that a total of 522 homeless
-    individual died in Toronto between November 2020 to June 2023.
+Homeless life is not easy, data from @Homeless_Death_Count shows that a
+total of 522 homeless individual died in Toronto between November 2020
+to June 2023. The Central Intake Line is created with the intend to help
+homeless individuals in need. It provides a 24/7 platform for
+individuals to receive government help. The insignificance of its
+influence suggests that the helpline has not fulfilled its intended
+purpose, though it is also important to note that having insignificant
+effect on reducing death count does not mean the helpline has not
+contributed to the well-being of Toronto's homeless population in other
+ways. The following two subsections discusses two of the possible
+factors that contributes to the insignificance of the helpline's
+influence on the reduction of homeless death in Toronto: inaccessibility
+to phone lines and substitute calling options.
 
--   The Central Intake Line is created with the intend to help homeless
-    individuals in need. It provides a 24/7 platform for individuals to
-    receive government help.
+### Inaccessibility of Phone Lines
 
--   The insignificance of its influence suggests that the helpline has
-    not fulfilled its intended purpose, though it is also important to
-    note that having insignificant effect on reducing death count does
-    not mean the helpline has not contributed to the well-being of
-    Toronto's homeless population in other ways.
+Difficulty in accessing the helpline may contribute to the
+insignificance of the influence the helpline has on the reduction of
+homeless death in Toronto. In order to access the resources provided by
+the helpline, a homeless individual is required to have access to one of
+the following three tools: mobile phone with valid phone plan, free
+city-run phone, or payphone. Financially, the most expensive option is
+the mobile phone. In 2024, the cheapest calling plan in Toronto starts
+at \$15 before tax, discouraging the less wealthy proportion of the
+homeless population. The cheapest alternative is the city-run free phone
+lines accessible in several City buildings and Universities across
+Toronto. According to @localwiki, there are currently 9 locations in
+downtown Toronto offering access to free phone lines. However, the free
+phone line access is only available during the operation hours of the
+respective buildings, meaning that free calls are not available 24/7.
+This leaves the last option, the affordable and readily available local
+payphones. Currently, Toronto payphones cost 50 cents per call, which is
+definitely more financially reasonable for the homeless population.
+However, numerous articles through the years have pointed out the steady
+decline of functional payphones in Toronto. The popularization of
+smartphones in the last decade contributes to the decrease in the demand
+of payphones, subsequently causing more and more abandoned or
+un-repaired payphone stations. This difficulty in accessing the helpline
+will decrease the number of callers, subsequently lowering the influence
+of the helpline on reducing homeless death in Toronto.
 
--   This makes us question
+### Substitute Calling Options
+
+The Central Intake Line is one of the biggest city-run homeless
+helplines in Toronto; however, it is not the only one. Using keywords
+“homeless helpline Toronto”, search results such as City of Toronto Line
+(311) and Assaulted Women’s Helpline also appear in the Google search
+engine. The existence of multiple helplines will cause specific problems
+to go to specific channels, reducing the total percent of homeless
+population that choose to use the Central Intake Line inquired in this
+paper. Similar to the previous factor, reduction in the total number of
+calls per month reduces the average influence of the helpline on the
+reduction of homeless death. Other potential factors that may contribute
+to the insignificance of influence are: changes in city policies, lack
+of promotion through non-internet platforms, etc.
 
@@
 
-Weaknesses: very small sample size, only 32 observations Next steps:
-investigate into the possible factors that caused a net zero impact on
-reduction of homeless death count and propose possible solution using
-data.
+The biggest weakness for this paper is the small sample size of the
+data, there are only 32 observations in the final data used for
+analysis. This suggests that resulting outputs may not accurately
+represent the situation in the real world because trends might only
+exist in our observed sample. Some potential next steps are:
+investigating into the proposed factors that contributes to the
+insignificance of helpline influence on homeless death using real-world
+data and models, as well as researching further into other potential
+factors.
 
@@
 
-# Additional data details
-
 # Model details {#sec-model-details}
@@
 In @fig-total-coded-model-ppcheckandposteriorvsprior-1 we implement a
-posterior predictive check. This shows...
+posterior predictive check. This shows a relatively close match between
+the regression outcome from our data and the simulation created by the
+posterior distribution. This suggests that our model is a relatively
+good fit for our data.
 
 In @fig-total-coded-model-ppcheckandposteriorvsprior-2 we compare the
-posterior with the prior. This shows...
+posterior with the prior. We can see that the estimation parameters
+shifts minimally after taking data into account. This suggests that good
+prior parameters were set.
 
@@
 In @fig-referred-informed-model-ppcheckandposteriorvsprior-1 we
-implement a posterior predictive check. This shows...
+implement a posterior predictive check. This shows a relatively close
+match between the regression outcome from our data and the simulation
+created by the posterior distribution. This suggests that our model is a
+relatively good fit for our data.
 
 In @fig-referred-informed-model-ppcheckandposteriorvsprior-2 we compare
-the posterior with the prior. This shows...
+the posterior with the prior. We can see that the estimation parameters
+shifts minimally after taking data into account. This suggests that good
+prior parameters were set.
 
@@
 
-@fig-total-coded-model-stanareyouokay-1 is a trace plot. It shows...
-This suggests...
+@fig-total-coded-model-stanareyouokay-1 is a trace plot. Trace plots are
+often used to diagnose abnormalities of models. In
+@fig-total-coded-model-stanareyouokay-1, lines are oscillating
+vertically and maintains an overall horizontal trend. This suggests that
+there is nothing out of the ordinary for our model.
 
-@fig-total-coded-model-stanareyouokay-2 is a Rhat plot. It shows... This
-suggests...
+@fig-total-coded-model-stanareyouokay-2 is a Rhat plot. Rhat plot is a
+valuable tool for assessing convergence in Bayesian regression models,
+helping ensure the reliability and validity of the model's inference
+results. In @fig-total-coded-model-stanareyouokay-2, all data points are
+close to 1. This suggest that there is nothing out of the ordinary for
+our model.
 
@@
 
-@fig-referred-informed-model-stanareyouokay-1 is a trace plot. It
-shows... This suggests...
+@fig-referred-informed-model-stanareyouokay-1 is a trace plot. Trace
+plots are often used to diagnose abnormalities of models. In
+@fig-referred-informed-model-stanareyouokay-1, lines are oscillating
+vertically and maintains an overall horizontal trend. This suggests that
+there is nothing out of the ordinary for our model.
 
-@fig-referred-informed-model-stanareyouokay-2 is a Rhat plot. It
-shows... This suggests...
+@fig-referred-informed-model-stanareyouokay-2 is a Rhat plot. Rhat plot
+is a valuable tool for assessing convergence in Bayesian regression
+models, helping ensure the reliability and validity of the model's
+inference results. In @fig-referred-informed-model-stanareyouokay-2, all
+data points are close to 1. This suggest that there is nothing out of
+the ordinary for our model.
 

### 2024-03-16 paper/paper.qmd
finished final rendering

@@
 bibliography: references.bib
-editor: 
-  markdown: 
-    wrap: 72
 ---
@@
 
-The City of Toronto has been consistently providing funding and staff in
-an effort to reduce the active homeless population within its governing
-district. Amongst numerous city efforts, the 24/7 helpline — Toronto
-Central Intake Line — was created to offer referrals to emergency
-shelters, sleeping accommodations, and provide general information about
-homelessness and prevention. [@Central_Intake_Call]. Starting in 2020,
-detailed data about the Central Intake Line became available on the
-OpenDataToronto portal [@OpenDataToronto].
+The City of Toronto has been consistently providing funding and staff in an effort to reduce the active homeless population within its governing district.
+Amongst numerous city efforts, the 24/7 helpline — Toronto Central Intake Line — was created to offer referrals to emergency shelters, sleeping accommodations, and provide general information about homelessness and prevention.
+[@Central_Intake_Call].
+Starting in 2020, detailed data about the Central Intake Line became available on the OpenDataToronto portal [@OpenDataToronto].
 
-The estimand of the paper focuses on examining the influence of helpline
-efforts on the reduction of homeless deaths in Toronto. Using Central
-Intake Call Wrap-up Codes data [@Central_Intake_Call] from
-OpenDataToronto [@OpenDataToronto], three different aspects of the
-helpline efforts were isolated: total calls coded, referral to shelter,
-and homelessness prevention information provided. These three key
-aspects were measured against the monthly cumulative death count from
-Deaths of People Experiencing Homelessness Data [@Homeless_Death_Count]
-documented by the Toronto Public Health [@TPH]. The analyses yielded an
-insignificant negative correlation between the net efforts of the
-helpline staff. The variable referral to shelter yields a positive
-correlation with homeless death count, whereas the effort to provide
-homelessness information yields a negative correlation. This implies
-that the net influence of helpline efforts is statistically negligible,
-while individual efforts can be productive or counterproductive. This
-examination in the net efforts and individual efforts can provide the
-helpline with a suggestion of which types of services or calls would be
-more economically efficient to allocate their labor resources on.
+The estimand of the paper focuses on examining the influence of helpline efforts on the reduction of homeless deaths in Toronto.
+Using Central Intake Call Wrap-up Codes data [@Central_Intake_Call] from OpenDataToronto [@OpenDataToronto], three different aspects of the helpline efforts were isolated: total calls coded, referral to shelter, and homelessness prevention information provided.
+These three key aspects were measured against the monthly cumulative death count from Deaths of People Experiencing Homelessness Data [@Homeless_Death_Count] documented by the Toronto Public Health [@TPH].
+The analyses yielded an insignificant negative correlation between the net efforts of the helpline staff.
+The variable referral to shelter yields a positive correlation with homeless death count, whereas the effort to provide homelessness information yields a negative correlation.
+This implies that the net influence of helpline efforts is statistically negligible, while individual efforts can be productive or counterproductive.
+This examination in the net efforts and individual efforts can provide the helpline with a suggestion of which types of services or calls would be more economically efficient to allocate their labor resources on.
 
-Analyses and findings in this paper are structured into several
-sections: @sec-data -- Data, @sec-model – Model, @sec-results --
-Results, and @sec-discussion -- Discussion. The Data section examines
-all datasets and variables kept for analysis, followed by an explanation
-of their data cleaning processes. The Model section defines linear
-models used for further analysis, explain its components, and presents
-model justifications. The Result section focuses on visualizing and
-presenting the model results through data presented in Data section. The
-Discussion section further evaluate the interpretations behind the model
-results presented in the previous section, and touches on any weaknesses
-and next steps.
+Analyses and findings in this paper are structured into several sections: @sec-data -- Data, @sec-model – Model, @sec-results -- Results, and @sec-discussion -- Discussion.
+The Data section examines all datasets and variables kept for analysis, followed by an explanation of their data cleaning processes.
+The Model section defines linear models used for further analysis, explain its components, and presents model justifications.
+The Result section focuses on visualizing and presenting the model results through data presented in Data section.
+The Discussion section further evaluate the interpretations behind the model results presented in the previous section, and touches on any weaknesses and next steps.
 
@@
 
-All data used in this paper are obtained through OpenDataToronto Portal
-[@OpenDataToronto]. Two different datasets: Central Intake Call Wrap-Up
-Codes Data [@Central_Intake_Call] and Deaths of People Experiencing
-Homelessness[@Homeless_Death_Count], are retrieved to analyze the effect
-of Toronto’s Central Call Line (denoted as *Helpline* for the remainder
-of this paper) efforts to the death counts of homeless individuals in
-Toronto. Data is cleaned and analyzed using the open source statistical
-programming language R [@citeR] and supporting packages tidyverse
-[@tidyverse], janitor [@janitor], rstanarm [@rstanarm], arrow [@arrow],
-ggplot2 [@ggplot2], and knitr [@knitr]. Detailed description of each
-dataset can be found in the subsections below.
+All data used in this paper are obtained through OpenDataToronto Portal [@OpenDataToronto].
+Two different datasets: Central Intake Call Wrap-Up Codes Data [@Central_Intake_Call] and Deaths of People Experiencing Homelessness[@Homeless_Death_Count], are retrieved to analyze the effect of Toronto’s Central Call Line (denoted as *Helpline* for the remainder of this paper) efforts to the death counts of homeless individuals in Toronto.
+Data is cleaned and analyzed using the open source statistical programming language R [@citeR] and supporting packages tidyverse [@tidyverse], janitor [@janitor], rstanarm [@rstanarm], arrow [@arrow], ggplot2 [@ggplot2], and knitr [@knitr].
+Detailed description of each dataset can be found in the subsections below.
 
@@
 
-On the OpenDataToronto portal, there are several datasets that reflect
-the City’s effort to shelter the local homeless population. The Central
-Intake Call Wrap-Up Codes Dataset [@Central_Intake_Call], stored in the
-Central Intake Calls Catalogue [@Central_Intake_Call], is one of the
-freshest and most detailed. Data is stored and published by the Shelter,
-Support & Housing Administration since November of 2020 and refreshes on
-a monthly basis. The latest refresh occurred on January 15th, 2024.
+On the OpenDataToronto portal, there are several datasets that reflect the City’s effort to shelter the local homeless population.
+The Central Intake Call Wrap-Up Codes Dataset [@Central_Intake_Call], stored in the Central Intake Calls Catalogue [@Central_Intake_Call], is one of the freshest and most detailed.
+Data is stored and published by the Shelter, Support & Housing Administration since November of 2020 and refreshes on a monthly basis.
+The latest refresh occurred on January 15th, 2024.
 
-The data set provides a daily summary of the number of calls received,
-the number of calls classified into distinct wrap-up codes by the nature
-of its issue, and a count of calls under each wrap-up code. One of the
-example wrap-up codes in the original data set was: *Code 1A - Referral
-to a Sleeping/Resting Space*. The original data set includes 13 distinct
-wrap-up codes; only two codes, *Code 1A — Referral to a Sleeping/Resting
-Space* and *Code 2C — Information - Homelessness & Prevention Services*,
-were chosen for our analysis. Code 1A and Code 2C are best suited as
-measurements for positive impact the Central Intake Line could provide
-because they provide a count of the number of callers provided with
-directions or advice. Other non-suitable wrap-up codes include: *Code
-1D - Declined Shelter/Resting Space*, *Code 4B - Disconnected - No
-Outcome*, etc.
+The data set provides a daily summary of the number of calls received, the number of calls classified into distinct wrap-up codes by the nature of its issue, and a count of calls under each wrap-up code.
+One of the example wrap-up codes in the original data set was: *Code 1A - Referral to a Sleeping/Resting Space*.
+The original data set includes 13 distinct wrap-up codes; only two codes, *Code 1A — Referral to a Sleeping/Resting Space* and *Code 2C — Information - Homelessness & Prevention Services*, were chosen for our analysis.
+Code 1A and Code 2C are best suited as measurements for positive impact the Central Intake Line could provide because they provide a count of the number of callers provided with directions or advice.
+Other non-suitable wrap-up codes include: *Code 1D - Declined Shelter/Resting Space*, *Code 4B - Disconnected - No Outcome*, etc.
 
-The final dataset only includes monthly cumulative data before July of
-2023. The rationalization behind the action will be explained in
-@sec-combined-data.
+The final dataset only includes monthly cumulative data before July of 2023. The rationalization behind the action will be explained in @sec-combined-data.
 
@@
 
-The Deaths of People Experiencing Homelessness Dataset
-[@Homeless_Death_Count] contains monthly cumulative records of homeless
-deaths. The dataset is published by Toronto Public Health [@TPH]. The
-earliest data record started in January of 2017, and the latest record
-ends in June of 2023.
+The Deaths of People Experiencing Homelessness Dataset [@Homeless_Death_Count] contains monthly cumulative records of homeless deaths.
+The dataset is published by Toronto Public Health [@TPH].
+The earliest data record started in January of 2017, and the latest record ends in June of 2023.
 
-The original dataset contains three columns: *Year of death*, *Month of
-death*, and *Count*. After careful inspection of raw data, any rows that
-containing an “unknown” value are excluded. Although this action created
-a source of error in future analyses, this is still a necessary step
-because we are plotting death counts against a timeline.
+The original dataset contains three columns: *Year of death*, *Month of death*, and *Count*.
+After careful inspection of raw data, any rows that containing an “unknown” value are excluded.
+Although this action created a source of error in future analyses, this is still a necessary step because we are plotting death counts against a timeline.
 
-Final dataset only includes data from November 2020 to June 2023
-(@tbl-death-count). The rationalization behind the action will be
-explained in @sec-combined-data.
+Final dataset only includes data from November 2020 to June 2023 (@tbl-death-count). The rationalization behind the action will be explained in @sec-combined-data.
 
@@
 
-During the data cleaning process, code was written to ensure that both
-the Central Intake Call Wrap-Up Codes Dataset [@Central_Intake_Call] and
-the Deaths of People Experiencing Homelessness Dataset
-[@Homeless_Death_Count] are filtered to include only data between 1st
-November, 2020 to 30st June, 2023.
+During the data cleaning process, code was written to ensure that both the Central Intake Call Wrap-Up Codes Dataset [@Central_Intake_Call] and the Deaths of People Experiencing Homelessness Dataset [@Homeless_Death_Count] are filtered to include only data between 1st November, 2020 to 30st June, 2023.
 
-The decision is reached by taking the common time period between the two
-datasets. In the latest refresh, the Central Intake Call Wrap-Up Codes
-Dataset [@Central_Intake_Call] begins on 3rd November, 2020 and end on
-31st December, 2023; whereas the Deaths of People Experiencing
-Homelessness Dataset [@Homeless_Death_Count] begins on January of 2017
-and ends on June 2023.
+The decision is reached by taking the common time period between the two datasets.
+In the latest refresh, the Central Intake Call Wrap-Up Codes Dataset [@Central_Intake_Call] begins on 3rd November, 2020 and end on 31st December, 2023; whereas the Deaths of People Experiencing Homelessness Dataset [@Homeless_Death_Count] begins on January of 2017 and ends on June 2023.
 
-The ultimate purpose of taking the common time period is to ensure that
-we can have the same amount of observations for analysis. Thus a
-combined dataset that kept the variables of interest in both datasets is
-created (@tbl-combined).
+The ultimate purpose of taking the common time period is to ensure that we can have the same amount of observations for analysis.
+Thus a combined dataset that kept the variables of interest in both datasets is created (@tbl-combined).
 
@@
 
-While we can still make claims on the correlations between helpline
-efforts and homeless death count without modelling, regression analysis
-is still necessary to provide rigorous backbones for a claim's
-statistical significance.
+While we can still make claims on the correlations between helpline efforts and homeless death count without modelling, regression analysis is still necessary to provide rigorous backbones for a claim's statistical significance.
 
-Here we briefly describe the Bayesian analysis model used to investigate
-the correlation between homeless death counts in Toronto and the efforts
-of the Helpline staff. Background details and diagnostics are included
-in [Appendix -@sec-model-details].
+Here we briefly describe the Bayesian analysis model used to investigate the correlation between homeless death counts in Toronto and the efforts of the Helpline staff.
+Background details and diagnostics are included in [Appendix -@sec-model-details].
 
@@
 
-Magnitude of effect created by the helpline efforts can be estimated
-through linear models. Gaussian regression model is best suited for our
-analytical purposes. Other generalized linear models such as Logistic
-and Multilevel are not considered due to the nature of the variables in
-interest. Logistic regression model requires data that yields either an
-**yes** or **no** result, whereas multilevel model require more
-complexity between variables. Due to the nature of the Poisson function,
-the Poisson model was considered and discarded because model results in
-extremely small values with no evidently different interpretations.
+Magnitude of effect created by the helpline efforts can be estimated through linear models.
+Gaussian regression model is best suited for our analytical purposes.
+Other generalized linear models such as Logistic and Multilevel are not considered due to the nature of the variables in interest.
+Logistic regression model requires data that yields either an **yes** or **no** result, whereas multilevel model require more complexity between variables.
+Due to the nature of the Poisson function, the Poisson model was considered and discarded because model results in extremely small values with no evidently different interpretations.
 
@@
 
-The Total Coded model estimates the the total helpline efforts against
-Toronto's homeless death count.
+The Total Coded model estimates the the total helpline efforts against Toronto's homeless death count.
 
@@
 
--   $y_i$ is the number of homeless death count in Toronto recorded by
-    @TPH per month
+-   $y_i$ is the number of homeless death count in Toronto recorded by @TPH per month
 
--   $\phi_i$ is the total number of calls received and coded by the
-    helpline per month
+-   $\phi_i$ is the total number of calls received and coded by the helpline per month
 
@@
 
-In case of oversimplification, a second model is proposed to isolate the
-effects of calls that refer individuals to shelter and calls that
-provide information on homelessness prevention.
+In case of oversimplification, a second model is proposed to isolate the effects of calls that refer individuals to shelter and calls that provide information on homelessness prevention.
 
@@
 
--   $y_i$ is the number of homeless death count in Toronto recorded by
-    @TPH per month
+-   $y_i$ is the number of homeless death count in Toronto recorded by @TPH per month
 
--   $\beta_i$ is the number of homeless individuals referred to shelters
-    through the helpline, per month
+-   $\beta_i$ is the number of homeless individuals referred to shelters through the helpline, per month
 
--   $\gamma_i$ is the number of individuals provided with information on
-    homelessness prevention through the helpline, per month
+-   $\gamma_i$ is the number of individuals provided with information on homelessness prevention through the helpline, per month
 
-We run the model in R [@citeR] using the `rstanarm` package of
-@rstanarm. We use the default priors from `rstanarm`.
+We run the model in R [@citeR] using the `rstanarm` package of @rstanarm. We use the default priors from `rstanarm`.
 
@@
 
-We expect a net negative relationship between the net efforts made by
-the helpline staff (Recorded by the Total_Coded) and homeless death
-count, which implies that net effect of helpline calls **reduces**
-homeless death count in Toronto.
+We expect a net negative relationship between the net efforts made by the helpline staff (Recorded by the Total_Coded) and homeless death count, which implies that net effect of helpline calls **reduces** homeless death count in Toronto.
 
-Additionally, we expect a negative relationship between homeless death
-and the two individual efforts: *number of homeless individuals referred
-to shelter*, and *number of individuals provided with homelessness
-prevention information*. Since both factors are coded efforts made by
-the helpline, both factors should also help to reduce homeless death
-count in Toronto.
+Additionally, we expect a negative relationship between homeless death and the two individual efforts: *number of homeless individuals referred to shelter*, and *number of individuals provided with homelessness prevention information*.
+Since both factors are coded efforts made by the helpline, both factors should also help to reduce homeless death count in Toronto.
 
@@
 
-Under the Gaussian regression model, @fig-total-coded illustrates a
-fitted line that estimates the linear relationship between the number of
-total calls coded and homeless death count in Toronto. The graph suggest
-that there exist a net negative correlation between the two variable.
-According to the graph, homeless death count decrease as total number of
-calls coded increase. The significance of this relationship is discussed
-below in in the model summary table.
+Under the Gaussian regression model, @fig-total-coded illustrates a fitted line that estimates the linear relationship between the number of total calls coded and homeless death count in Toronto.
+The graph suggest that there exist a net negative correlation between the two variable.
+According to the graph, homeless death count decrease as total number of calls coded increase.
+The significance of this relationship is discussed below in in the model summary table.
 
@@
 ```
-
-The model summary table, @tbl-modelresults, displays the coefficient
-values of the predictor variables against response variable: homeless
-death count in Toronto. Coefficients of predictors indicate their
-influence against the response variable. For example, the column on the
-left shows that, under Model 1, every 1 additional helpline call coded
-and decrease the homeless death count by 0.0003. The ***+p \<...***
-section at the bottom of the table represents statistically significance
-of the coefficient values. As indicated by the ***+p\<...*** legend, the
-coefficients with 1 \*, coefficient is significant at 95% confidence
-level; for \*\*, coefficient is significant at 99% confidence level, and
-so on. However, as we can see from the table below, no \* exists for the
-coefficients in both models.
 
@@
 
+The model summary table, @tbl-modelresults, displays the coefficient values of the predictor variables against response variable: homeless death count in Toronto.
+Coefficients of predictors indicate their influence against the response variable.
+For example, the column on the left shows that, under Model 1, every 1 additional helpline call coded and decrease the homeless death count by 0.0003.
+The ***+p \<...*** section at the bottom of the table represents statistically significance of the coefficient values.
+As indicated by the ***+p\<...*** legend, the coefficients with 1 \*, coefficient is significant at 95% confidence level; for \*\*, coefficient is significant at 99% confidence level, and so on.
+However, as we can see from the table below, no \* exists for the coefficients in both models.
+
 # Discussion {#sec-discussion}
@@
 
--   On average, for every increase in calls coded by the helpline, there
-    is a 0.0003 unit decrease in homeless death in Toronto. There is an
-    overall reduction, albeit very small, in homeless death as the
-    number of total coded calls increase. This implies that the helpline
-    need to take at minimum 3333 calls per month to save 1 homeless life
-    in Toronto. On average, the helpline takes 14828.59 calls per month,
-    meaning that 4.45 lives are saved on average.
--   4.45 is not a significant number in both a practical and statistical
-    sense. To improve the return on total number of calls coded, we
-    attempted to identify promising call codes that contribute to the
-    net positive reduction in homeless death. Out of the 13 different
-    call codes, *Referral to Shelter* and *Information on Homeless
-    Prevention* are best suited as individual efforts of measurement for
-    positive impacts because they provide a count of the number of
-    callers provided with directions or advice. For every caller
-    provided with information on homeless prevention information, there
-    is an average decrease of 0.0048 death count in Toronto. On the
-    other hand, for every homeless caller referred to shelter, there is
-    a 0.0059 unit of average **increase** in homeless death in Toronto.
-    This trend is very counter-intuitive and discouraging at first
-    glance. In the case where the correlation is more significant, we
-    would want to further analyze factor related to referrals to
-    shelter. Accuracy on the current status of shelters, level of detail
-    on instructed, and misjudgment of shelter eligibility are possible
-    factors of examination. However, since the effect of this call code
-    is statistically insignificant, it is also likely to be just a fluke
-    of observation.
+On average, for every increase in calls coded by the helpline, there is a 0.0003 unit decrease in homeless death in Toronto.
+There is an overall reduction, albeit very small, in homeless death as the number of total coded calls increase.
+This implies that the helpline need to take at minimum 3333 calls per month to save 1 homeless life in Toronto.
+On average, the helpline takes 14828.59 calls per month, meaning that 4.45 lives are saved on average.
+
+4.45 is not a significant number in both a practical and statistical sense.
+To improve the return on total number of calls coded, we attempted to identify promising call codes that contribute to the net positive reduction in homeless death.
+Out of the 13 different call codes, *Referral to Shelter* and *Information on Homeless Prevention* are best suited as individual efforts of measurement for positive impacts because they provide a count of the number of callers provided with directions or advice.
+For every caller provided with information on homeless prevention information, there is an average decrease of 0.0048 death count in Toronto.
+On the other hand, for every homeless caller referred to shelter, there is a 0.0059 unit of average **increase** in homeless death in Toronto.
+This trend is very counter-intuitive and discouraging at first glance.
+In the case where the correlation is more significant, we would want to further analyze factor related to referrals to shelter.
+Accuracy on the current status of shelters, level of detail on instructed, and misjudgment of shelter eligibility are possible factors of examination.
+However, since the effect of this call code is statistically insignificant, it is also likely to be just a fluke of observation.
 
@@
 
-Homeless life is not easy, data from @Homeless_Death_Count shows that a
-total of 522 homeless individual died in Toronto between November 2020
-to June 2023. The Central Intake Line is created with the intend to help
-homeless individuals in need. It provides a 24/7 platform for
-individuals to receive government help. The insignificance of its
-influence suggests that the helpline has not fulfilled its intended
-purpose, though it is also important to note that having insignificant
-effect on reducing death count does not mean the helpline has not
-contributed to the well-being of Toronto's homeless population in other
-ways. The following two subsections discusses two of the possible
-factors that contributes to the insignificance of the helpline's
-influence on the reduction of homeless death in Toronto: inaccessibility
-to phone lines and substitute calling options.
+Homeless life is not easy, data from @Homeless_Death_Count shows that a total of 522 homeless individual died in Toronto between November 2020 to June 2023.
+The Central Intake Line is created with the intend to help homeless individuals in need.
+It provides a 24/7 platform for individuals to receive government help.
+The insignificance of its influence suggests that the helpline has not fulfilled its intended purpose, though it is also important to note that having insignificant effect on reducing death count does not mean the helpline has not contributed to the well-being of Toronto's homeless population in other ways.
+The following two subsections discusses two of the possible factors that contributes to the insignificance of the helpline's influence on the reduction of homeless death in Toronto: inaccessibility to phone lines and substitute calling options.
 
@@
 
-Difficulty in accessing the helpline may contribute to the
-insignificance of the influence the helpline has on the reduction of
-homeless death in Toronto. In order to access the resources provided by
-the helpline, a homeless individual is required to have access to one of
-the following three tools: mobile phone with valid phone plan, free
-city-run phone, or payphone. Financially, the most expensive option is
-the mobile phone. In 2024, the cheapest calling plan in Toronto starts
-at \$15 before tax, discouraging the less wealthy proportion of the
-homeless population. The cheapest alternative is the city-run free phone
-lines accessible in several City buildings and Universities across
-Toronto. According to @localwiki, there are currently 9 locations in
-downtown Toronto offering access to free phone lines. However, the free
-phone line access is only available during the operation hours of the
-respective buildings, meaning that free calls are not available 24/7.
-This leaves the last option, the affordable and readily available local
-payphones. Currently, Toronto payphones cost 50 cents per call, which is
-definitely more financially reasonable for the homeless population.
-However, numerous articles through the years have pointed out the steady
-decline of functional payphones in Toronto. The popularization of
-smartphones in the last decade contributes to the decrease in the demand
-of payphones, subsequently causing more and more abandoned or
-un-repaired payphone stations. This difficulty in accessing the helpline
-will decrease the number of callers, subsequently lowering the influence
-of the helpline on reducing homeless death in Toronto.
+Difficulty in accessing the helpline may contribute to the insignificance of the influence the helpline has on the reduction of homeless death in Toronto.
+In order to access the resources provided by the helpline, a homeless individual is required to have access to one of the following three tools: mobile phone with valid phone plan, free city-run phone, or payphone.
+Financially, the most expensive option is the mobile phone.
+In 2024, the cheapest calling plan in Toronto starts at \$15 before tax, discouraging the less wealthy proportion of the homeless population.
+The cheapest alternative is the city-run free phone lines accessible in several City buildings and Universities across Toronto.
+According to @localwiki, there are currently 9 locations in downtown Toronto offering access to free phone lines.
+However, the free phone line access is only available during the operation hours of the respective buildings, meaning that free calls are not available 24/7.
+This leaves the last option, the affordable and readily available local payphones.
+Currently, Toronto payphones cost 50 cents per call, which is definitely more financially reasonable for the homeless population.
+However, numerous articles through the years have pointed out the steady decline of functional payphones in Toronto.
+The popularization of smartphones in the last decade contributes to the decrease in the demand of payphones, subsequently causing more and more abandoned or un-repaired payphone stations.
+This difficulty in accessing the helpline will decrease the number of callers, subsequently lowering the influence of the helpline on reducing homeless death in Toronto.
 
@@
 
-The Central Intake Line is one of the biggest city-run homeless
-helplines in Toronto; however, it is not the only one. Using keywords
-“homeless helpline Toronto”, search results such as City of Toronto Line
-(311) and Assaulted Women’s Helpline also appear in the Google search
-engine. The existence of multiple helplines will cause specific problems
-to go to specific channels, reducing the total percent of homeless
-population that choose to use the Central Intake Line inquired in this
-paper. Similar to the previous factor, reduction in the total number of
-calls per month reduces the average influence of the helpline on the
-reduction of homeless death. Other potential factors that may contribute
-to the insignificance of influence are: changes in city policies, lack
-of promotion through non-internet platforms, etc.
+The Central Intake Line is one of the biggest city-run homeless helplines in Toronto; however, it is not the only one.
+Using keywords “homeless helpline Toronto”, search results such as City of Toronto Line (311) and Assaulted Women’s Helpline also appear in the Google search engine.
+The existence of multiple helplines will cause specific problems to go to specific channels, reducing the total percent of homeless population that choose to use the Central Intake Line inquired in this paper.
+Similar to the previous factor, reduction in the total number of calls per month reduces the average influence of the helpline on the reduction of homeless death.
+Other potential factors that may contribute to the insignificance of influence are: changes in city policies, lack of promotion through non-internet platforms, etc.
 
@@
 
-The biggest weakness for this paper is the small sample size of the
-data, there are only 32 observations in the final data used for
-analysis. This suggests that resulting outputs may not accurately
-represent the situation in the real world because trends might only
-exist in our observed sample. Some potential next steps are:
-investigating into the proposed factors that contributes to the
-insignificance of helpline influence on homeless death using real-world
-data and models, as well as researching further into other potential
-factors.
+The biggest weakness for this paper is the small sample size of the data, there are only 32 observations in the final data used for analysis.
+This suggests that resulting outputs may not accurately represent the situation in the real world because trends might only exist in our observed sample.
+Some potential next steps are: investigating into the proposed factors that contributes to the insignificance of helpline influence on homeless death using real-world data and models, as well as researching further into other potential factors.
 
@@
 
-In @fig-total-coded-model-ppcheckandposteriorvsprior-1 we implement a
-posterior predictive check. This shows a relatively close match between
-the regression outcome from our data and the simulation created by the
-posterior distribution. This suggests that our model is a relatively
-good fit for our data.
+In @fig-total-coded-model-ppcheckandposteriorvsprior-1 and @fig-referred-informed-model-ppcheckandposteriorvsprior-1, we implement a posterior predictive check.
+This shows a relatively close match between the regression outcome from our data and the simulation created by the posterior distribution.
+This suggests that our model is a relatively good fit for our data.
 
-In @fig-total-coded-model-ppcheckandposteriorvsprior-2 we compare the
-posterior with the prior. We can see that the estimation parameters
-shifts minimally after taking data into account. This suggests that good
-prior parameters were set.
+In @fig-total-coded-model-ppcheckandposteriorvsprior-2 and @fig-referred-informed-model-ppcheckandposteriorvsprior-2, we compare the posterior with the prior.
+We can see that the estimation parameters shifts minimally after taking data into account.
+This suggests that good prior parameters were set.
 
@@
 ```
-
-In @fig-referred-informed-model-ppcheckandposteriorvsprior-1 we
-implement a posterior predictive check. This shows a relatively close
-match between the regression outcome from our data and the simulation
-created by the posterior distribution. This suggests that our model is a
-relatively good fit for our data.
-
-In @fig-referred-informed-model-ppcheckandposteriorvsprior-2 we compare
-the posterior with the prior. We can see that the estimation parameters
-shifts minimally after taking data into account. This suggests that good
-prior parameters were set.
 
@@
 
-@fig-total-coded-model-stanareyouokay-1 is a trace plot. Trace plots are
-often used to diagnose abnormalities of models. In
-@fig-total-coded-model-stanareyouokay-1, lines are oscillating
-vertically and maintains an overall horizontal trend. This suggests that
-there is nothing out of the ordinary for our model.
+@fig-total-coded-model-stanareyouokay-1 and @fig-total-coded-model-stanareyouokay-2 are trace plots.
+Trace plots are often used to diagnose abnormalities of models.
+For both plots, lines are oscillating vertically and maintains an overall horizontal trend.
+This suggests that there is nothing out of the ordinary for our model.
 
-@fig-total-coded-model-stanareyouokay-2 is a Rhat plot. Rhat plot is a
-valuable tool for assessing convergence in Bayesian regression models,
-helping ensure the reliability and validity of the model's inference
-results. In @fig-total-coded-model-stanareyouokay-2, all data points are
-close to 1. This suggest that there is nothing out of the ordinary for
-our model.
+@fig-total-coded-model-stanareyouokay-2 and @fig-referred-informed-model-stanareyouokay-2 are Rhat plots.
+Rhat plot is a valuable tool for assessing convergence in Bayesian regression models, helping ensure the reliability and validity of the model's inference results.
+Both both plots, all data points are close to 1.
+This suggest that there is nothing out of the ordinary for our model.
 
@@
 ```
-
-@fig-referred-informed-model-stanareyouokay-1 is a trace plot. Trace
-plots are often used to diagnose abnormalities of models. In
-@fig-referred-informed-model-stanareyouokay-1, lines are oscillating
-vertically and maintains an overall horizontal trend. This suggests that
-there is nothing out of the ordinary for our model.
-
-@fig-referred-informed-model-stanareyouokay-2 is a Rhat plot. Rhat plot
-is a valuable tool for assessing convergence in Bayesian regression
-models, helping ensure the reliability and validity of the model's
-inference results. In @fig-referred-informed-model-stanareyouokay-2, all
-data points are close to 1. This suggest that there is nothing out of
-the ordinary for our model.
 
